Online Multiclass Linear Classification with Bandit Feedback

### 2018-11-13 arxiv-version/main.tex
Add algorithm for strongly separable case

\begin{figure}
\begin{center}
\input{figures/linearly-separable-examples-with-margin}
\end{center}
\caption{The figure shows labeled examples in $\R^2$ that are linearly separable with a
positive margin $\gamma$. There are $K=3$ classes. The examples of each class
are colored white, gray and black respectively. All examples lie in the ball of
radius $R$ centered at the origin. However, the examples are \emph{not} strongly
linearly separable for any positive margin $\gamma$.
}
\label{figure:linearly-separable-examples-with-margin}
\end{figure}

@@

>>>>

\begin{figure}
\begin{center}
\input{figures/linearly-separable-examples-with-margin}
\end{center}
\caption{The figure shows labeled examples in $\R^2$. There are $K=3$ classes. The
examples of each class are colored white, gray and black respectively. All
examples lie in the ball of radius $R$ centered at the origin. While the
examples are linearly separable with a positive margin $\gamma$, they are
\emph{not} strongly linearly separable for any positive margin $\gamma$,
however.
}
\label{figure:linearly-separable-examples-with-margin}
\end{figure}

@@

\begin{algorithm}[h]
\caption{Algorithm for strongly linearly separable examples
\label{algorithm:algorithm-for-strongly-linearly-separable-examples}}
\begin{algorithmic}[1]
{
\REQUIRE{Number of classes $K$}
\STATE{Initialize $w_1^{(1)} = w_2^{(1)} = \dots = w_K^{(1)} = 0$}
\FOR{$t=1,2,\dots$}
\STATE{Receive feature vector $x_t$}
\STATE{Compute $S_t = \{ i ~:~ \ip{w_i^{(t)}}{x_t} > 0 \}$}
\IF{$|S_t| = 1$}
\STATE{Predict $\widehat y_t$ where $\widehat y_t \in S_t$}
\ELSE
\STATE{Predict $\widehat y_t \sim \text{Uniform}(\{1,2,\dots,K\})$}
\ENDIF
\STATE{Receive feedback $z_t \in \{0,1\}$ where $z_t = \indicator{\widehat y_t = y_t}$}
\STATE{Update $w_i^{(t+1)} = w_i^{(t)}$ for all $i \in \{1,2,\dots,K\} \setminus \{\widehat y_t\}$}
\IF{$z_t = 0$}
\STATE{Update $w_{\widehat y_t}^{(t+1)} = w_{\widehat y_t}^{(t)} - x_t$}
\ELSE
\STATE{Update $w_{\widehat y_t}^{(t+1)} = w_{\widehat y_t}^{(t)}$}
\ENDIF
\ENDFOR
}
\end{algorithmic}
\end{algorithm}

\begin{theorem}
Let $(V, \ip{\cdot}{\cdot})$ be any inner product space, let $K$ be a positive
integer, $\gamma$ a positive real number, $R$ be a non-negative real number
If $(x_1, y_1), (x_2, y_2), \dots, (x_T, y_T)$ is a sequence of labeled examples
in $V \times \{1,2,\dots,K\}$ such that the examples are strongly separable with
margin $\gamma$ and $\norm{x_1}, \norm{x_2}, \dots, \norm{x_T} \le R$ then
Algorithm~\ref{algorithm:algorithm-for-strongly-linearly-separable-examples}
makes at most $K (R/\gamma)^2$ mistakes.
\end{theorem}

\begin{proof}
TODO
\end{proof}
